Deciding Bitvector Termination with Program Synthesis

### 2014-07-02 papers/termination/paper.tex
Some nontermination

@@

In order to formulate the non-termination problem inside the synthesis fragment, 
we make use of the notion of \emph{closed recurrence set} introduced by Chen et al. in \cite{DBLP:conf/tacas/ChenCFNO14}. 
As opposed to a closed recurrence set, this is a  purely universal property: for each state in the recurrence set $N$, each of its successors 
must be in $N$. Thus, the non-termination problem becomes equivalent to the
satisfiability of Definition~\ref{def:deterministic-nonterm-formula}.
As our formulation is with respect to a given loop $L=\langle I,G,t \rangle$, we require the  
recurrence set to include the loop's guard, $N(x) \rightarrow G(x)$. In other words, the loop's guard needs to be satisfied in order for the 
infinite execution to happen.

@@

\section{Genetic Programming and Incremental Evolution}

>>>>

Dually to termination, we might want to consider the non-termination of a program.  If a program terminates,
we can prove this by finding a ranking function and supporting invariant witnessing the satisfiability
of formula {\bf[CT]}.  What then would a proof of non-termination look like?

@@

In order to formulate the non-termination problem inside the synthesis fragment, 
we make use of the notion of \emph{closed recurrence set} introduced by Chen et al. in \cite{DBLP:conf/tacas/ChenCFNO14}. 
As opposed to a closed recurrence set, this is a $\exists \forall$ property: for each state in the recurrence set $N$, all of its successors 
must be in $N$. We note that if $T$ is deterministic, every open recurrence set is also a closed recurrence set (since each
state has at most one successor).  Thus, the non-termination problem for deterministic transition systems is equivalent to the
satisfiability of Definition~\ref{def:deterministic-nonterm-formula}.
As our formulation is with respect to a given loop $L=\langle I,G,t \rangle$, we require the  
recurrence set to include the loop's guard, $N(x) \rightarrow G(x)$. In other words, the loop's guard needs to be satisfied in order for the 
infinite execution to happen.

@@

\subsection{Genetic Programming and Incremental Evolution}
